### 2017-07-21 README.Rmd

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![codecov.io](https://codecov.io/github/ropensci/EML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/EML?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/EML?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/EML)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/EML)](http://cran.r-project.org/package=EML)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/EML)](https://CRAN.R-project.org/package=EML)
[![Github Stars](https://img.shields.io/github/stars/ropensci/EML.svg?style=social&label=Github)](https://github.com/ropensci/EML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

>>>>

[![Travis-CI Build Status](https://travis-ci.org/ropensci/EML.svg?branch=master)](https://travis-ci.org/ropensci/EML)
[![codecov.io](https://codecov.io/github/ropensci/EML/coverage.svg?branch=master)](https://codecov.io/github/ropensci/EML?branch=master)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/ropensci/EML?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/EML)
[![](https://ropensci.org/badges/80_status.svg)](https://github.com/ropensci/onboarding/issues/80)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/EML)](https://cran.r-project.org/package=EML)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/EML)](https://CRAN.R-project.org/package=EML)
[![DOI](https://zenodo.org/badge/10894022.svg)](https://zenodo.org/badge/latestdoi/10894022)

<!--
[![Github Stars](https://img.shields.io/github/stars/ropensci/EML.svg?style=social&label=Github)](https://github.com/ropensci/EML)
-->
